\section{Experience}
\subsection{Vocational}
\cventry{2016--2018}{Tech Lead, Software Engineer}{Siroop AG}{Zürich}{}{Developing product information management solution
\newline{}%
\newline{}%
Details:%
\begin{itemize}%
\item Creating an auto-scaling and serverless product information processing pipeline
\item Maintaining and improving existing systems - dockerization, automatic deployments, refactoring and quality assurance by automated tests
\item Leading a team of developers
\item On-call duty
\item Working in an agile way, using scrum and later kanban
\item Requirements engineering
\item Extreme programming
\newline{}%
\end{itemize}
\textit{Technologies used}: python, javascript, AWS cloud, serverless, microservices, datadog, linux, docker, docker-compose, terraform
}

\cventry{2016}{Software Developer}{Liip AG}{Zürich}{}{Software Engineer, Web-Applications with Tapestry 4.1 and Playframework with connections to various ERP-Systems (SAP via ISA or JCO, Navision, Performis, CRHtrade etc.). Designing Import-Systems from PIM (IDAS, ASIM, Stibo, Tradcom etc.)
\newline{}%
\newline{}%
One \textbf{Highlight} was that I could redesign and implement a legacy sequential import system to a parallel one, reducing the duration from 12 hours to 30 Minutes!
\newline{}%
\newline{}%
Detailed accomplishments:%
\begin{itemize}%
\item Replaced legacy deployment strategy with a custom maven 2 plugin.
\item Serving as an expert examiner for apprentice exams.
\item Migrationg SCM from Subversion to git
\item Leading internal workshops for 
\begin{itemize}
\item Unit Testing 
\item Software Quality
\item Maven2
\end{itemize}
\item Design and Implementing various interfaces from the web-application to third-party systems (ERP)
\item Design runtime and import infrastructure with docker (www.docker.io)
\item Technical Lead in the development group
\item Architectural Design
\item Support of Junior-Developers
\item Conducting job interviews and coding assessments
\item Maintenance/Bugfixing/Enhancements of existing projects
\end{itemize}
\textit{Technologies used}: Java, Scala, Javascript, MSSQL, Oracle, JBoss, Apache Lucene, elasticsearch, XSLT, STX, Webservices/REST, Maven2, SBT, Jenkins, web-frameworks like Play and Tapestry, Html, CSS, bash, linux, docker}
\cventry{2006--2008}{Freelancer}{}{Zürich}{}{Creating, developping, maintaining and hosting of websites/cms.\newline
{}Creation of an online comic-shop.\newline
\textit{Technologies used}: PHP, Apache, Linux, Symfony
}
\cventry{2005--2006}{Assistant}{ETH Zürich}{Zürich}{}{Assistant 
\begin{itemize}%
\item Prof. R. Hiptmair, D-Math \begin{itemize}%
\item Working on paper for lecture \emph{Numerical Mathematic for Computational Science} in \LaTeX
\item Scripts in Perl, \LaTeX and Bash for statistics.
\end{itemize}
\item Prof. W. van Gunsteren, IGC \newline Working on lecture papers.
\end{itemize}
\textit{Technologies used}: Bash, Perl, Subversion, \LaTeX
}
\cventry{2003--2004}{Assistant, Tutor}{University of Zürich}{Zürich}{}
{Part time employee\newline{}Teaching java to beginners}


\subsection{Miscellaneous}
\cventry{2004}{Call-Agent}{DIMAZ AG}{Zürich}{}{Customer care on french/german}
\cventry{2001--2002}{Clerk}{Zentralstelle für Lohnnachzahlungen (ZLBG)}{Zürich}{}{Clerk}
\cventry{1997--2001}{Employee}{Swissport Ag}{Zürich Kloten}{Airport Zürich}{Part time job during graduation}
